Masterclass Assignment: Real-time Global Illumination

### 2018-01-12 docs/paper.tex
typo

Unfortunately I wasn't able to implement a sparse data structure as described in the source material \cite{crassinneyretsainzgreeneisemann2011} before the assignment deadline. Having a sparse data structure to store the emissive voxel texture would save a significant amount of GPU memory consumption, allowing the resolution for voxelization to be much higher; currently dense 3D textures it is capable of hitting the 2 gigabyte memory limit of my GPU.

>>>>

Unfortunately I wasn't able to implement a sparse data structure as described in the source material \cite{crassinneyretsainzgreeneisemann2011} before the assignment deadline. Having a sparse data structure to store the emissive voxel texture would save a significant amount of GPU memory consumption, allowing the resolution for voxelization to be much higher; currently with dense 3D textures it is capable of exceeding both the 2 gigabyte memory limit of my GPU, and the 8 gigabyte limit of those at university.
